Analytic Light Curves in Reflected Light

### 2020-03-29 tex/ms.tex
added I proof

%
\begin{figure}[t!]
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/speed.pdf}
        \oscaption{speed}{%
            Evaluation time for the starry algorithm.
            \label{fig:speed}
        }
    \end{centering}
\end{figure}

@@

\subsection{$\mathcal{J}_v$}
%
The function $\mathcal{J}_v$ is given by
%
\begin{align}
    \label{eq:J}
    \mathcal{J}_v(k^2, \kap) =
    \sum_{i = 0}^{\frac{N - 1}{2}}
    \int\limits_{\frac{1}{2}\kappa_{2i}}^{\frac{1}{2}\kappa_{2i+1}}
    \sin^{2v}\varphi
    \left(1 - \frac{\sin^2\varphi}{k^2}\right)^\frac{3}{2}
    \mathrm{d}\varphi
    \quad.
\end{align}
%
The integral in this expression is the same as that in Equation (D39)
of \citet{Luger2019}, except for a change in the limits of integration.
In that paper, we computed all terms
$\{ \mathcal{J}_0, {\cdot\cdot\cdot}, \mathcal{J}_\vmax \}$ from a three-term
recurrence relation and two boundary conditions. In the case of upward
recursion, the boundary conditions $\mathcal{J}_0$ and $\mathcal{J}_1$ were
computed analytically from the complete elliptic integrals $K(k^2)$
and $E(k^2)$. In cases where upward recursion was not numerically stable, we
evaluated $\mathcal{J}_\vmax$ and $\mathcal{J}_{\vmax-1}$
via a quickly convergent series expansion and recursed downward.

>>>>

%
\begin{figure}[h!]
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/speed.pdf}
        \oscaption{speed}{%
            Evaluation time for the starry algorithm.
            \label{fig:speed}
        }
    \end{centering}
\end{figure}

@@

\subsection{$\mathcal{I}_v$}
%
The function $\mathcal{I}_v$ is given by
%
\begin{align}
    \label{eq:I}
    \mathcal{I}_v(k^2, \kap) =
    \sum_{i = 0}^{\frac{N - 1}{2}}
    \int\limits_{\frac{1}{2}\kappa_{2i}}^{\frac{1}{2}\kappa_{2i+1}}
    \sin^{2v}\varphi
    \mathrm{d}\varphi
    \quad.
\end{align}
%
The integral in this expression is the same as that in Equation (D38)
of \citet{Luger2019}, except for a change in the limits of integration.
As in \citet{Luger2019}, we can compute this integral recursively given
a trivial lower boundary condition:
%
\begin{proof}{I}
    \label{eq:Irec}
    \mathcal{I}_0(\kap) &=
    \frac{\Delta \kap}{2}
    %
    \nonumber \\
    %
    \mathcal{I}_v(\kap) &=
    \frac{1}{2v}
    \bigg(
    (2v - 1) \mathcal{I}_{v-1}(\kap) -
    \Delta \left(\sin^{2v - 1}\left(\frac{\kap}{2}\right)
    \cos\left(\frac{\kap}{2}\right)\right)
    \bigg)
\end{proof}
%
where the last expression is valid for all $v > 0$. We find that this algorithm
is generally stable, except when $\sin\left(\frac{\kap}{2}\right)$ is small. In
that limit, we evaluate $\mathcal{I}_N(\kap)$ by numerical integration of
Equation~(\ref{eq:I}) using Gauss-Legendre quadrature with \STARRYQUADPOINTS
points. We then recurse downward by substituting $v \rightarrow v + 1$ in
Equation~(\ref{eq:Irec}) and solving for $\mathcal{I}_v(\kap)$.

\subsection{$\mathcal{J}_v$}
%
The function $\mathcal{J}_v$ is given by
%
\begin{align}
    \label{eq:J}
    \mathcal{J}_v(k^2, \kap) =
    \sum_{i = 0}^{\frac{N - 1}{2}}
    \int\limits_{\frac{1}{2}\kappa_{2i}}^{\frac{1}{2}\kappa_{2i+1}}
    \sin^{2v}\varphi
    \left(1 - \frac{\sin^2\varphi}{k^2}\right)^\frac{3}{2}
    \mathrm{d}\varphi
    \quad.
\end{align}
%
The integral in this expression is again the same as that in Equation (D39)
of \citet{Luger2019}, except for a change in the limits of integration.
In that paper, we computed all terms
$\{ \mathcal{J}_0, {\cdot\cdot\cdot}, \mathcal{J}_\vmax \}$ from a three-term
recurrence relation and two boundary conditions. In the case of upward
recursion, the boundary conditions $\mathcal{J}_0$ and $\mathcal{J}_1$ were
computed analytically from the complete elliptic integrals $K(k^2)$
and $E(k^2)$. In cases where upward recursion was not numerically stable, we
evaluated $\mathcal{J}_\vmax$ and $\mathcal{J}_{\vmax-1}$
via a quickly convergent series expansion and recursed downward.
